---
title: MLOps
subtitle: Welcome to our course!
author: Jan Kirenz
format:
  revealjs:
    theme: default
    transition: fade
    slide-number: true
    chalkboard:
      buttons: false
    preview-links: auto
    logo: images/logo.png
    css: styles.css
    footer: '<https://mlops-ss23.github.io/website/>'
    incremental: true 
#jupyter: python3
---

```{r}
#| echo: false

library(countdown)
```


## Welcome!

- Name, current job, your major in the masters program
- What do you hope to get out of this course?
- Anything you want to share/ask?

```{r}
countdown(minutes = 8)
```


## Resources


![Designing Machine Learning Systems by Chip Huyen, released May 2022](https://www.oreilly.com/library/view/designing-machine-learning/9781098107956/)



## Take the survey

- Go to the course website: <https://mlops-ss23.github.io/website/>

- Click on the instructions for Lab 0 on the course schedule

- Take the *Getting to know you* survey

## Assignments

- Txt



## Wrap up

Any questions about the course?


